\documentclass[10pt,a4paper,sans]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[scale=0.85]{geometry} 
\setlength{\hintscolumnwidth}{2.7cm}
\usepackage{lmodern}
\usepackage[T1]{fontenc}

\renewcommand*{\namefont}{\fontsize{18}{22}\mdseries\upshape} 
\renewcommand*{\titlefont}{\fontsize{10}{12}\mdseries\upshape} 

\name{Fabien}{Furfaro}
\title{Lead Data \& AI Engineer}
\email{fabien.furfaro@gmail.com}
\phone[mobile]{+33 6 66 92 16 76}
\social[linkedin]{fabien-furfaro}
\social[github]{fabienfrfr}

\begin{document}
\makecvtitle
\vspace*{-10mm}

\section{Profile}


With a PhD in Physics specializing in computer vision and statistics, I have a strong background in electronics, gained at Enedis and Vinci. My experience includes designing and implementing AI optimization solutions, leading reinforcement learning and generative AI projects at Capgemini, and developing recommendation systems based on constrained optimization at Thales. Currently, I lead pre-sales and solution architecture for aerospace clients.

\section{Key Skills}

\cvitem{}{%
\textbf{Technical:} AI, ML, Deep Learning, Reinforcement Learning, Generative AI, NLP, Computer Vision, Anomaly Detection, Constrained Optimization, Python, PyTorch, TensorFlow, Simulink, MLFlow, Azure, Docker, GitLab, CAN Bus.\\
\textbf{Functional:} Research \& Science, Agile PM, V-cycle, Backlog Refinement, Business model, MLOps.\\
\textbf{Languages:} French (native), English (professional)
}

\section{Professional Experience}

\cventry{06/2025--Present}
{AI Expert}{Aerospace}{}{}{%
  \begin{small}
  \begin{itemize}%
    \item Technical lead on AI topics for 3D image-based resetting projects.
  \end{itemize}
  \end{small}%
}{Pre-Sales Solution Architect}{}{}{%
\begin{small}
\begin{itemize}%
  \item Collaborated with sales teams to translate business needs into technical solutions and demos. %
  \item Designed and presented technical architectures for proposals and developed proof-of-concept to support strategic decision-making.%
\end{itemize}
\end{small}%


\cventry{01/2025--06/2025}{Lead Data Scientist}{Capgemini}{}{}{%
  \begin{small}
  \begin{itemize}%
    \item Architected a recommendation system integrating constrained optimization and anomaly detection.%
    \item Managed ML and data industrialization in defense environment.%
  \end{itemize}
  \end{small}%
}

\cventry{06/2024--01/2025}{Senior Data Scientist}{Thales Group}{}{}{%
  \begin{small}
  \begin{itemize}%
    \item Developed and deployed machine learning and deep learning solutions from data to production.%
    \item Managed MLOps, statistics, and agile workflows.%
  \end{itemize}
  \end{small}%
}


\cventry{09/2022--09/2024}{Project Leader - AI Researcher}{Capgemini Engineering (APA)}{}{}{%
  \begin{small}
  \begin{itemize}%
    \item Developed automotive cooling systems and intelligent supervision.%
    \item Led project management and research activities.%
  \end{itemize}
  \end{small}%
}

\cventry{09/2019--09/2022}{Machine Learning Researcher}{INSEP / CNAM}{}{}{%
  \begin{small}
  \begin{itemize}%
    \item Created evolutionary algorithms for neural network functionalization.%
  \end{itemize}
  \end{small}%
}

\cventry{04/2014--09/2014}{Internship in Biotech}{ENS (Grande écoles)}{}{}{
  \begin{small}
  \begin{itemize}%
    \item Studied the collective behavior of bacteria using game theory.%
  \end{itemize}
  \end{small}%
}


\cventry{2008--2012}{Electronic Designer}{Axians (Vinci) / ERDF (Enedis)}{}{}{}

\section{Education}

\cventry{2015--2019}{PhD in Physics, specializing in Complex Systems}{Université de Paris Cité}{}{}{
\begin{small}
  \begin{itemize}%
    \item How to control and track cell differentiation in microfluidics chip.%
  \end{itemize}
  \end{small}%
}

\cventry{2013--2015}{Master’s Degree in Applied Physics}{Université de Paris Cité}{}{}{}

\cventry{2012--2013}{Bachelor's Degree in Physics}{Université Paris Diderot}{}{}{}

\cventry{2010--2012}{BTS in Electrotechnics}{Lycée St Nicolas}{}{}{}

\end{document}
